paper

### 2021-09-14 paper.Rmd
as

```{r}
new_dt %>% 
  group_by(herbicide) %>% 
  summarise(biomass = mean(biomass_gm2, na.rm = TRUE),
            counts = sd(biomass_gm2, na.rm = TRUE))
```

>>>>

```{r}
new_dt %>% 
  group_by(herbicide, location) %>% 
  summarise(biomass = mean(biomass_gm2, na.rm = TRUE),
            sd = sd(biomass_gm2, na.rm = TRUE)) %>% 
  filter(location == "Brooklyn")
```
